---
title: "p8105_hw6_ys3508"
output: github_document
date: "2022-12-3"

---
# HW6
```{r}
library(tidyverse)
library(viridis)
library(purrr)
library(modelr)


knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```

In this example, the $\hat{r}^2$ value is high, and the upper bound at 1 may be a cause for the generally skewed shape of the distribution. If we wanted to construct a confidence interval for $R^2$, we could take the 2.5% and 97.5% quantiles of the estimates across bootstrap samples. However, because the shape isn't symmetric, using the mean +/- 1.96 times the standard error probably wouldn't work well.

We can produce a distribution for $\log(\beta_0 * \beta1)$ using a similar approach, with a bit more wrangling before we make our plot.

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

As with $r^2$, this distribution is somewhat skewed and has some outliers. 

The point of this is not to say you should always use the bootstrap -- it's possible to establish "large sample" distributions for strange parameters / values / summaries in a lot of cases, and those are great to have. But it is helpful to know that there's a way to do inference even in tough cases. 

## Problem 2

### Clean the dataset
```{r, show_col_types = FALSE}
# Import the dataset
homicide <- read_csv(url("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"), na = c("", "NA", "Unknown"))

homicide = homicide %>%
  janitor::clean_names() %>%
  mutate(
    reported_date = as.Date(as.character(reported_date), format = "%Y%m%d"),
    city_state = str_c(city, ", ", state),
    victim_race = fct_relevel(victim_race, "White"),
    victim_age = as.numeric(victim_age),
    status = case_when(
      disposition == "Closed by arrest"      ~ "resolved",
      disposition == "Closed without arrest" ~ "unresolved",
      disposition == "Open/No arrest"        ~ "unresolved",
      TRUE                                   ~ ""
    )
  ) %>% 
  filter(!city_state %in% c("Dallas, TX","Phoenix, AZ","Kansas City, MO","Tulsa, AL"),
  victim_race %in% c("White","Black"))
  
```

