---
title: "p8105_hw6_ys3508"
output: github_document
date: "2022-12-3"

---
# HW6
install new package
```{r}
# install.packages('leaps')
```
load library
```{r}


library(tidyverse)
library(viridis)
library(purrr)
library(modelr)
library(leaps)


knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```

In this example, the $\hat{r}^2$ value is high, and the upper bound at 1 may be a cause for the generally skewed shape of the distribution. If we wanted to construct a confidence interval for $R^2$, we could take the 2.5% and 97.5% quantiles of the estimates across bootstrap samples. However, because the shape isn't symmetric, using the mean +/- 1.96 times the standard error probably wouldn't work well.

We can produce a distribution for $\log(\beta_0 * \beta1)$ using a similar approach, with a bit more wrangling before we make our plot.

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

As with $r^2$, this distribution is somewhat skewed and has some outliers. 

The point of this is not to say you should always use the bootstrap -- it's possible to establish "large sample" distributions for strange parameters / values / summaries in a lot of cases, and those are great to have. But it is helpful to know that there's a way to do inference even in tough cases. 

## Problem 2

### Clean the dataset
```{r, show_col_types = FALSE}
# Import the dataset
homicide <- read_csv(url("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"), na = c("", "NA", "Unknown"))

homicide = homicide %>%
  janitor::clean_names() %>%
  mutate(
    reported_date = as.Date(as.character(reported_date), format = "%Y%m%d"),
    city_state = str_c(city, ", ", state),
    victim_race = fct_relevel(victim_race, "White"),
    victim_age = as.numeric(victim_age),
    status = case_when(
      disposition == "Closed by arrest"      ~ 0,
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 1,
)
  ) %>% 
  filter(!city_state %in% c("Dallas, TX","Phoenix, AZ","Kansas City, MO","Tulsa, AL"),
  victim_race %in% c("White","Black"))
  
```

### Fit a logistic regression
```{r}
logistic = homicide %>%
    filter(city_state == "Baltimore, MD") %>% 
    glm(status ~ victim_age + victim_race + victim_sex, data = ., family = "binomial") 
    
logistic %>% 
    broom::tidy() %>% 
  mutate(OR = exp(estimate),
         CI_lower = exp(estimate - 1.96 * std.error),
         CI_upper = exp(estimate + 1.96 * std.error)) %>% 
  select(term, estimate, OR, CI_lower,CI_upper) %>% 
  knitr::kable(digits = 3, 
        col.names = c("Term", "Log(OR)", "Estimated adjusted OR", "CI lower bound", "CI upper bound"))

```

### Nesting city
```{r}
nest_city = homicide %>%  
  nest(df = -city_state) %>% 
  mutate(models = map(.x = df, ~ glm(status ~ victim_age + victim_race + victim_sex, data = .x, family = "binomial")),
    results = map(models, broom::tidy)) %>% 
  select(city_state, results) %>% 
   unnest(results) %>% 
  mutate(OR = exp(estimate),
         CI_lower = exp(estimate - 1.96 * std.error),
         CI_upper = exp(estimate + 1.96 * std.error)) %>% 
  filter(term == "victim_sexMale") %>% 
  select(city_state, OR, CI_lower,CI_upper)

nest_city %>% 
  knitr::kable(digits = 3, 
        col.names = c("Term", "Estimated adjusted OR", "CI lower bound", "CI upper bound")) 

```

### Plot that shows the estimated ORs and CIs
```{r}
plot <-nest_city %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>%
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) +
  labs(x = "City and state", 
       y = "Estimated OR with CI",
       title = "Solving homicides comparing male victims to female victims in each city \nEstimated Adjusted OR with 95% CI") +
  theme(axis.text.x = element_text(angle = 80, hjust = 1))

plot
ggsave(
  plot,
  filename = "figures/plot.png")

```

## Problem 3
### Load and clean data
```{r}
birthweight = read_csv("./data/birthweight.csv")

birthweight <- birthweight %>% 
  janitor::clean_names() %>%
  mutate(babyset = as.factor(babysex),
         frace = as.factor(frace),
         malform = as.factor(malform),
         mrace = as.factor(mrace)) %>% 
  mutate(babysex = recode(babysex, "1" = "male", "2" = "female"),
         frace = recode(frace, 
                        "1" = "White", 
                        "2" = "Black", 
                        "3" = "Asian", 
                        "4" = "Puerto Rican", 
                        "8" = "Other", 
                        "9" = "Unknown"),
         malform = recode(malform, "0" = "absent", "1" = "present"),
         mrace = recode(mrace, 
                        "1" = "White", 
                        "2" = "Black", 
                        "3" = "Asian", 
                        "4" = "Puerto Rican", 
                        "8" = "Other"))
```
check nas
```{r}
sum(is.na(birthweight))
```

### Building linear regression model
**Step 1: Perform linear regression with all predictors**
```{r}

lm1 <- lm(bwt ~ ., data = birthweight)
summary(lm1)
```
With all of our variables included in the model, the base adjusted r² is 0.717 and the Residual Standard Error is 272.5. This relationship is significant at the P<.05 level.

**Step 2: Run the `regsubsets()` function on all variables**
```{r}
best_predictors <-
    regsubsets(bwt ~.,
               data = birthweight,
               nbest = 1,      # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
summary_best_predictors <- summary(best_predictors)

```

**Step 3: Choose number of predictors**
```{r}
which.max(summary_best_predictors$adjr2)
```

**Step 4: Choose best predictors**
```{r}
summary_best_predictors$which[15,]
```

The best model fit for linear regression model:`babysexmale`, `bhead`, `blength`, `fincome`,`gaweeks`,`menarche`,`mheigh`,`mrace`,`parity`,`ppbmi`,`smoken`,`wtgain`